Quasi-Monte Carlo Methods: What, Why, and How?

### 2025-01-14 HickernellMCQMC2024_QMCTutorial.tex
txs auto checkin

Although error bound \eqref{eq:cuberrbd} is elegant, it leaves several questions unanswered:
\begin{itemize}
	\item The reproducing kernel, $K$, defined both the discrepancy and the variation.  This means that differnt choices of $K$ will lead to different error bounds for the same $\hat{\mu}_n$, even though the error is unchanged.
	\item The Hilbert space
\end{itemize}

@@

>>>>

Although error bound \eqref{eq:cuberrbd} is elegant, it leaves several matters unresolved:
\begin{itemize}
	\item The reproducing kernel $K$ defines both the discrepancy and the variation.  This means that differnt choices of $K$ will lead to different error bounds for the same $\hat{\mu}_n$, even though the error is unchanged.
	\item The Hilbert space $\calH_K$ contains ones assumptions about $f$, such as smoothness or periodicity. Knowing $K$, however, does not automatically lead to an explict formula for the inner product of the associated Hilbert space, $\langle \cdot, \cdot \rangle_{\calH_K}$.  Conversely, having an explict formula for  $\langle \cdot, \cdot \rangle_{\calH_K}$ does not automatically lead to an explict formula for the reproducing kernel, $K$.  In both cases educated guesswork is involved.
	\item Choosing a more restrictive $\calH_K$ may lead to a sharper error bound, however, it is often infeasible in practice to check whether the ``black box'' $f$ lies in $\calH_K$.
	\item   Moreover, even if one is confident that $f \in \calH_K$, it is usually impractical to compute variation$(f,K)$, as we shall see below.  Error bound \eqref{eq:cuberrbd} cannot be used as a stopping criterion to determine the $n$ needed to satisfy an error tolerance.
\end{itemize}
Nonetheless \eqref{eq:cuberrbd}

@@

\subsection{Randomized Error}
